RDA trait prediction tutorial

### 2023-02-10 DGE_comparison_v2.Rmd
re-rendered website (minus some cached files too large for now) with katie's rda tutorial page

```{r setup, include = FALSE}
# should remove from Rmd
# Set root directory
#knitr::opts_knit$set(root.dir = '~/Documents/GitHub/DGE_comparison/')

@@

#invisible(lapply(c( "tidyverse", "ape", "vegan", "GGally",
                   #, "rgl", "adegenet", "MASS",
                   #"data.table", "plyr", "lmtest", "reshape2", "Rmisc", "lmerTest","statmod"),
                 #function(p){
                   #if(! p %in% rownames(installed.packages())) {
                     #install.packages(p)
                  # }
                  # library(p, character.only=TRUE)
                 #}))

>>>>

```{r setup, include = FALSE}
# should remove from Rmd
# Set root directory
#knitr::opts_knit$set(root.dir = '~/Documents/GitHub/DGE_comparison/')
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

@@

#invisible(lapply(c( "tidyverse", "ape", "vegan", "GGally",
                   #"rgl", "adegenet", "MASS",
                   #"data.table", "plyr", "lmtest", "reshape2", "Rmisc", "lmerTest","statmod"),
                 #function(p){
                   #if(! p %in% rownames(installed.packages())) {
                     #install.packages(p)
                   #}
                   #library(p, character.only=TRUE)
                 #}))

### 2023-02-10 RDAtraitPredictionTutorial.Rmd
re-rendered website (minus some cached files too large for now) with katie's rda tutorial page

---
title: "RDA trait prediction tutorial"
author: "KE Lotterhos"
date: "2023-02-08"
output: pdf_document
---

@@

If the following packages are not installed, be sure to install them first:
```
install.packages("vegan")
install.packages("lfmm")

@@

The six environmental variables are based on real data from western Canada and are shown below, clockwise from upper right: Clockwise from upper left: precipitation of driest month, precipitation of warmest quarter, mean annual temperature, precipitation of wettest month, mean temperature of wettest quarter, mean temperature of driest quarter. Each small square is a simulated individual, with its color representing its trait value in that environment.

@@

G <- read.table(unz("Genotypes.txt.zip", "Genotypes.txt"))
dim(G) # 1000 individuals and 26371 loci

ind <- read.table("Individuals.txt", header=TRUE)
dim(ind) #corresponds to rows in G
head(ind)

muts <-  read.table("SNPs.txt", header=TRUE)
dim(muts) #corresponds to columns in G
head(muts)

>>>>

---
title: "RDA trait prediction tutorial"
author: "KE Lotterhos"
date: "2023-02-08"
output:
  html_document:
    df_print: paged
---

@@

If the following packages are not installed, be sure to install them first:
```
install.packages("vegan")
install.packages("lfmm")
install.packages("gplots")

@@

The six environmental variables are based on real data from western Canada and are shown below, clockwise from upper right: Clockwise from upper left: precipitation of driest month, precipitation of warmest quarter, mean annual temperature, precipitation of wettest month, mean temperature of wettest quarter, mean temperature of driest quarter. Background colors correspond to the optimum trait value on each landscape, and each small square is a simulated individual, with its color representing its trait value in that environment.

@@

G <- read.table(unz("rda_tutorial/Genotypes.txt.zip", "Genotypes.txt"))
dim(G) # 1000 individuals and 26371 loci

ind <- read.table("rda_tutorial/Individuals.txt", header=TRUE)
dim(ind) #corresponds to rows in G
head(ind)

muts <-  read.table("rda_tutorial/SNPs.txt", header=TRUE)
dim(muts) #corresponds to columns in G
head(muts)
